Discon analysis

### 2018-08-16 analysis/01_analysis.Rmd
kid experiment, summary markdown file

```{r data preprocessing}
# Data pre-processing

@@

ggplot(plot1,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(~distribution, 
             labeller = as_labeller(c(`c(6, 0, 0)` = "Distribution\n(6-0-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")

```
# How does the last item seen affect the object chosen in the anaphora case? 
```{r}
plot2 <- data %>%
  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
  mutate(trackLast = ifelse(lastInputCat == target1, "yes", "no")) %>%
  group_by (distribution, workerid) %>%
  summarise (lastInput = mean(same_lastInput),
             n = n()) %>% 
  multi_boot_standard(col = "lastInput")

@@

ggplot(plot2,
       aes(x = distribution, y = mean, fill = distribution)) +
  geom_bar(stat='identity', width = 0.3) +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few()
```
# Does the graded distribution come through in cases where the last input does not affect the object choice?
```{r}
plot3 <- data %>%
  filter(phase == "test", distribution == "c(4, 2, 0)", same_lastInput == 0) %>%
  group_by(distribution, workerid) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid) %>%
  group_by(distribution, item) %>%
  multi_boot_standard(col = "prop_correct")

@@

# 30/59 trials picking the same category as the last input slide.
# 24/33 for 4, 2, 0
# 7/26 for 2, 2, 2

>>>>

#Pilot 1 data
```{r data preprocessing}
# Data pre-processing

@@

ggplot(plot1,
       aes(x = item, y=mean, fill=item)) +
  geom_bar(stat='identity') +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  scale_fill_solarized(name = "Chosen item",
                       breaks = c("correct", "correct2", "correct3"),
                       labels = c("most frequent", "second most frequent", "least frequent"))+
  facet_grid(~distribution, 
             labeller = as_labeller(c(`c(5, 1, 0)` = "Distribution\n(5-1-0)", `c(4, 2, 0)` = "Distribution\n(4-2-0)", `c(2, 2, 2)` = "Distribution\n(2-2-2)", preference = "preference", statistical = "statistical"))) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) +
  labs(x="", y= "proportion chosen")
```
# How does the last item seen affect the object chosen in the anaphora case? 
```{r}
plot2 <- data %>%
  filter(phase == "test", distribution != "c(6, 0, 0)") %>%
  mutate(trackLast = ifelse(lastInputCat == target1, "yes", "no")) %>%
  group_by (distribution, workerid) %>%
  summarise (lastInput = mean(same_lastInput),
             n = n()) %>% 
  multi_boot_standard(col = "lastInput")

@@

ggplot(plot2,
       aes(x = distribution, y = mean, fill = distribution)) +
  geom_bar(stat='identity', width = 0.3) +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  geom_hline(yintercept = 1/3, lty=2) +
  ylim(0, 1) +
  theme_few()
```

# Are there 2 strategies in determining what "another one" means?
```{r}
plot3 <- data %>%
  filter(phase == 'test') %>%
  group_by(distribution, workerid) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid) %>%
  group_by(distribution, item)

plot3a <- plot3 %>%
  multi_boot_standard(col = "prop_correct")

ggplot() +
  geom_jitter(data = plot3, aes(x = item, y = prop_correct, col = distribution, alpha = .2), width = .3,height = .025)+
  geom_pointrange(data = plot3a, aes(x = item, y = mean, col = distribution, ymin = ci_lower, ymax = ci_upper),size = .8)+
  facet_grid(~distribution)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Item Chosen", y="Proportion Chosen")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
 # theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))

#No - if 2 strategies: there should be fewer dots in the middle
```
# Does where (5,1,0) occurs determine the strategy of chosing the last item?
```{r}
plot3 <- data %>%
  filter(phase == 'test', distribution == "c(5, 1, 0)") %>%
  mutate(distType = ifelse(trial < 4, "early", "late")) %>%
  group_by(distribution, workerid, distType) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid, -distType) %>%
  group_by(distribution, item, distType)

plot3a <- plot3 %>%
  multi_boot_standard(col = "prop_correct")

ggplot() +
  geom_jitter(data = plot3, aes(x = item, y = prop_correct, col = distribution, alpha = .2), width = .3,height = .025)+
  geom_pointrange(data = plot3a, aes(x = item, y = mean, col = distribution, ymin = ci_lower, ymax = ci_upper),size = .8)+
  facet_grid(~distType)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Item Chosen", y="Proportion Chosen")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
 # theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Does the graded distribution come through in cases where the last input does not affect the object choice?
```{r}
plot3 <- data %>%
  filter(phase == "test", distribution == "c(4, 2, 0)", same_lastInput == 0) %>%
  group_by(distribution, workerid) %>%
  summarise(correct = mean(correct_target1),
            correct2 = mean(correct_target2),
            correct3 = mean(correct_target3)) %>%
  gather(item, prop_correct, -distribution, -workerid) %>%
  group_by(distribution, item) %>%
  multi_boot_standard(col = "prop_correct")

@@

# 30/59 trials picking the same category as the last input slide.
# 24/33 for 4, 2, 0
# 7/26 for 2, 2, 2
```
